A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-02-25 main.tex
Lipton: mind-brain-body system

% 其實文章真正的目標是  bioinformatics workflow，而不是 discovered biomarkers itself (see TCGA marker paper\cite{Lawrence2015a})
Moreover, this bioinformatics paper provides targets and supports the community's rationale for looking into these HNSCC candidates by in vitro and in vivo validation. %Collectively, these findings provide new insights into HNSCC and suggest that shared and unique alterations might be leveraged to accelerate progress in prevention and therapy across tumour types\cite{Lawrence2015a}.
%We open invitation for research community by potential support their rationale for looking into these HNSCC candidates.
%邀請科學家們一塊兒來繼續研究下去找出幫助癌症患者的方法
%the rest of the analysis seems fine, but 
%文章的初衷、跨領域：如同deep leaning Keras API，推廣給研究者一個有效的方法 
We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on the TCGA or other in-house HNSCC datasets. % to find more useful biomarkers. % or even other cancer types
% to allow successful repetition and extension of analyses based on original data
A good research reproducibility practice is necessary to allow the reuse of code and results for new projects.
%previously developed methodology to be effectively applied on new data, or to allow 
%reuse of code and results for new projects. %In other words, good habits of reproducibility
It may turn out to be a time-saver in the longer run.
When multiple scientists can reproduce a result, it will also validate our initial results and readiness to progress to the next research phase. 
%why reproducibility?
%Reproducible Bioinformatics Project provides a general schema and an infrastructure to distribute robust and reproducible workflows. Thus, it guarantees to final users the ability to repeat any analysis independently using UNIX-like architecture.
%Utility of this model would facilitate development of more individualized therapy for HNSCC patients and improve prognosis.
Once our laboratory or the community confirms those candidates as the targets, the compound screening could facilitate more individualized therapy for HNSCC patients.
%and improve prognosis.

\subsubsection{Holistic cancer care}
Bruce Lipton: the biology of belief 信念的力量
biowell 勿膨脹自我: 我非常擔心，所謂的科學實驗，研究的疾病，發明的藥物，都會潛藏一種危機，因為它的療效與科學證據，都是建立在「意識統一場域」中，科學家在研究時，一定希望有效，能夠發現別人沒有發現且有用的事情，所以「成功」還是會帶有「人為的意念」。
那麼，這個結果不「公正」。甚至，當原來藥物發明者的心念改變了，（開始只想賺錢），那麼藥物的作用就更無法掌握。
也許，藥物副作用會很嚴重。而目前科學的解釋是，只是因為個體的基因差異。所以我們的科學家依舊在研究，基因對癌症的影響（單向）。
冤親債主的意念
TCGA treated by surgery and more; TNM available yes
discussion: limitation
Even there are many $X_1 ... X_n$ physical and social features of patients available for survival modelling in the TCGA.
 since it has comprehensive clinical features, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
the TCGA does not collect holistic features
Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, 
or even spiritual, emotional, and social status) go holistic

@@

Lipton 1992, epinephrine and histamine signals in endothelium, 心智作用
The microenvironment of HNSCC requires further exploration and understanding using a multiparametric approach.

[Results] In summary, those 20 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort. The important input $X_1...X_n$ should be patients' features: age, specific 20 gene expressions, clinical T stage, and surgical margin.
依舊是以管窺天
% https://link.springer.com/referenceworkentry/10.1007%2F978-1-4419-1428-6_575
%癌症與身心靈的重要關係：中醫、citation? emotional centered approach
PCA and ECA
Carl Rogers: Carl Rogers' person-centered theory
the therapist is providing the appropriate social-environmental conditions \cite{Rogers1957}.\cite{Joseph2004}\cite{Griffiths2013}
Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers\cite{Rogers1957}.
The research implication is to investigate the relationship between the client’s intrinsic motivation to explore his or her trauma-related thoughts and feelings and the nature of the therapeutic relationship as defined by the six conditions\cite{Rogers1957}.
Dealing with negative emotions. As the client feels intense negative emotions of fear, despair, sadness and so on, it is not the client-centred therapist’s task to try and remove these feelings: The task is simply to stay with the client’s experiences. T he research implication is to investigate the necessity and sufficiency of the six conditions.

@@

*** make Figure 5 holistic:
meridian and emotion has mutual reaction
meridian effect tissue and organ
(autonomic nerve system, myofascial network, prefrontal cortex)
placebo-effect influence on drug discovery
博士班學生，越研究越發現，科學的不足
，心理與靈性的力量，更是背後推動的冥冥力量
身心靈是合一的。#正念 除了可以減壓，還可以治癒疼痛

@@

prefrontal lobe 理智腦 意識 正念 杏仁核
「安慰劑」placebo effect，也已經有科學證明，與醫師、病患的意識（前額葉）功能，非常有關係。這也是負責同理心與愛的腦區。
物理作用、信號，雷射針灸
Therapeutic Relationship
Spirituality
慈悲心 compassion 
同情心 sympathy
同理心 empathy
non-verbal contact
前額葉內側 (medial prefrontal cortex)
額葉底部(orbitofrontal cortex)
治療關係的核心條件: 說好話 眼對眼 engaging 用真心
empowering
(一)雙方有心理的接觸。
(二)當事人正感到焦慮或不一致(incongruence)。 
(三)治療者在治療關係中是一致的、真實的或真誠的。
(四)治療者能夠對當事人表現出無條件的正向關懷。
(五)治療者能夠同理的瞭解當事人的內在，並努力傳達「我懂你的」。
Personhood: Carl Rogers
尋找生命的意義
真誠、能深刻地善解人意
非認知性核心能力
正念止觀(在當下)
人人有自癒能力
真誠 (Genuineness/Validity/Bona Fides)
內在聲音與外在態度一致/明心見性/超越的意識狀態
(Congruence/Consistency)
共情理解(設身處地/同理心/除我執)
(Empathic Understanding of Reference/Track)
無條件關懷(不批判/頓悟)
(unconditional positive regard)
***引導出案主的無條件自我關懷 => 療癒/復原力（resilience）
諮商員的
靈性功力
治療關係
I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing. Then simply my presence is releasing and helpful\cite{Rogers1979}.
%當最接近我的內在、直覺的自我，當我與我內在那不知名的角落（the unknown in me）接觸時(靈性)，當我有一些不一樣的意識狀態時（明心見性），我發現，單純只是我的存在（presence）就能鬆綁案主而且具有療效的。
%Rogers, C. R. The Foundations of the Person-Centered Approach. Education 100, 98–107 (1979).
「診後說三句，更勝良帖十方」

Warburg effect and carcinogenesis
cancer therapy by 患者自癒
Mindfullness Meditation help 復原力（resilience）
Self-Compassion  慈悲
Self-compassion 
除我執
 global self-esteem:
自戀（narcissism）1. Neff, K. D. & Vonk, R. Self-compassion versus global self-esteem: Two different ways of relating to oneself. J. Pers. 77, 23–50 (2009).\cite{Neff2009}

@@

mindfulness and meditation for cancer
情志養生 悲喜憂思苦 七情
人俯仰於天地之間
順從四季氣候變化
保養正氣陶冶性情
自我療癒身心靈疾病
%自他不二 心存正念 向內看，解決苦之源
%1.衷心懺悔
%2.真心感謝
%3.誠意祝福
%4.永存善念 慈悲
%5.心無恐懼: 情志養生
每位醫師都可以成為「創傷知情者」
幫助我們身邊的病患， 懂他的心靈創傷
讓他有安全感， 才有機會改變疾病的走向

@@

@@

>>>>

% 其實文章真正的目標是  bioinformatics workflow，而不是 discovered biomarkers itself (see TCGA marker paper\cite{Lawrence2015a})
Moreover, this bioinformatics paper provides targets and supports the community's rationale for looking into these HNSCC candidates by in vitro and in vivo validation. %Collectively, these findings provide new insights into HNSCC and suggest that shared and unique alterations might be leveraged to accelerate progress in prevention and therapy across tumour types\cite{Lawrence2015a}.
%We open invitation for research community by potential support their rationale for looking into these HNSCC candidates.
%邀請科學家們一塊兒來繼續研究下去找出幫助癌症患者的方法
%the rest of the analysis seems fine, but 
%文章的初衷、跨領域：如同deep leaning Keras API，推廣給研究者一個有效的方法 
We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on the TCGA or other in-house HNSCC datasets. % to find more useful biomarkers. % or even other cancer types
% to allow successful repetition and extension of analyses based on original data
A good research reproducibility practice is necessary to allow the reuse of code and results for new projects.
%previously developed methodology to be effectively applied on new data, or to allow 
%reuse of code and results for new projects. %In other words, good habits of reproducibility
It may turn out to be a time-saver in the longer run.
When multiple scientists can reproduce a result, it will also validate our initial results and readiness to progress to the next research phase. 
%why reproducibility?
%Reproducible Bioinformatics Project provides a general schema and an infrastructure to distribute robust and reproducible workflows. Thus, it guarantees to final users the ability to repeat any analysis independently using UNIX-like architecture.
%Utility of this model would facilitate development of more individualized therapy for HNSCC patients and improve prognosis.
Once our laboratory or the community confirms those candidates as the targets, the compound screening\cite{Yang2004}\cite{Hsu2011}\cite{Pathak2021} could facilitate more individualized therapy for HNSCC patients.
%and improve prognosis.
% 1. Pathak, N. et al. Uncovering flexible active site conformations of SARS-COV-2 3Cl proteases through protease pharmacophore clusters and covid-19 drug repurposing. ACS Nano 15, 857–872 (2021). 陽明交大

\subsubsection{Holistic cancer care} % by epigenetic control (placebo), person-central approach, PCA

TCGA treated by surgery and more; TNM available yes
discussion: limitation
Even there are many $X_1 ... X_n$ physical and social features of patients available for survival modelling in the TCGA.
 since it has comprehensive clinical features, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
the TCGA does not collect holistic features
Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, 
or even spiritual, emotional, and social status) go holistic

@@

Lipton introduced mind-brain-body system.
Lipton 1992, epinephrine and histamine signals in endothelium, %心智作用
 In a state of fear, the brain releases chemicals associated with fear, which are stress hormones and inflammatory agents.
dopamine, oxytocin, vasopressin, and growth hormone will be released by central nerve system in response to the perception of love.

Epigenetics control says that genetic expression is directly due to the environment and our perception of the environment\cite{Gustafson2017}.
The microenvironment of HNSCC requires further exploration and understanding using a multiparametric approach.
Bruce Lipton: the biology of belief %信念的力量
placebo effect and the old belief of genetic determinism\cite{Gustafson2017}
%biowell 勿膨脹自我: 我非常擔心，所謂的科學實驗，研究的疾病，發明的藥物，都會潛藏一種危機，因為它的療效與科學證據，都是建立在「意識統一場域」中，科學家在研究時，一定希望有效，能夠發現別人沒有發現且有用的事情，所以「成功」還是會帶有「人為的意念」。
%那麼，這個結果不「公正」。甚至，當原來藥物發明者的心念改變了，（開始只想賺錢），那麼藥物的作用就更無法掌握。也許，藥物副作用會很嚴重。而目前科學的解釋是，只是因為個體的基因差異。
genetic determinism 所以我們的科學家依舊在研究，基因對癌症的影響（單向）
The genetics of the cell give us all kinds of potentials. % 自性空

%冤親債主的意念 unknown X factors
[Results] In summary, those 10 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in \acrshort{hnscc}.
Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort. The important input $X_1...X_n$ should be patients' features: age, specific 20 gene expressions, clinical T stage, and surgical margin.
依舊是以管窺天
% https://link.springer.com/referenceworkentry/10.1007%2F978-1-4419-1428-6_575
%癌症與身心靈的重要關係：中醫、citation? emotional centered approach

PCA and ECA
Carl Rogers: Carl Rogers' person-centered theory
the therapist is providing the appropriate social-environmental conditions \cite{Rogers1957}.\cite{Joseph2004}\cite{Griffiths2013}
Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers\cite{Rogers1957}.
The research implication is to investigate the relationship between the client’s intrinsic motivation to explore his or her trauma-related thoughts and feelings and the nature of the therapeutic relationship as defined by the six conditions\cite{Rogers1957}.
Dealing with negative emotions. As the client feels intense negative emotions of fear, despair, sadness and so on, it is not the client-centred therapist’s task to try and remove these feelings: The task is simply to stay with the client’s experiences. T he research implication is to investigate the necessity and sufficiency of the six conditions.

@@

*** make Figure 5 holistic:
meridian and emotion has mutual reaction
meridian effect tissue and organ
(autonomic nerve system, myofascial network, prefrontal cortex)
placebo-effect influence on drug discovery
博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的。#正念 除了可以減壓，還可以治癒疼痛

@@

prefrontal lobe 理智腦 意識 正念 杏仁核 prefrontal cortex runs conscious mind
「安慰劑」placebo effect，也已經有科學證明，與醫師、病患的意識（前額葉）功能，非常有關係。這也是負責同理心與愛的腦區。
物理作用、信號，雷射針灸
Therapeutic Relationship
Spirituality
慈悲心 compassion 
同情心 sympathy
同理心 empathy
non-verbal contact
前額葉內側 (medial prefrontal cortex)
額葉底部(orbitofrontal cortex)
治療關係的核心條件: 說好話 眼對眼 engaging 用真心
empowering
(一)雙方有心理的接觸。
(二)當事人正感到焦慮或不一致(incongruence)。 
(三)治療者在治療關係中是一致的、真實的或真誠的。
(四)治療者能夠對當事人表現出無條件的正向關懷。
(五)治療者能夠同理的瞭解當事人的內在，並努力傳達「我懂你的」。
Personhood: Carl Rogers
尋找生命的意義
真誠、能深刻地善解人意
非認知性核心能力
正念止觀(在當下)
人人有自癒能力
真誠 (Genuineness/Validity/Bona Fides)
內在聲音與外在態度一致/明心見性/超越的意識狀態
(Congruence/Consistency)
共情理解(設身處地/同理心/除我執)
(Empathic Understanding of Reference/Track)
無條件關懷(不批判/頓悟)
(unconditional positive regard)
***引導出案主的無條件自我關懷 => 療癒/復原力（resilience）
諮商員的
靈性功力
治療關係
I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing. Then simply my presence is releasing and helpful\cite{Rogers1979}.
%當最接近我的內在、直覺的自我，當我與我內在那不知名的角落（the unknown in me）接觸時(靈性)，當我有一些不一樣的意識狀態時（明心見性），我發現，單純只是我的存在（presence）就能鬆綁案主而且具有療效的。
%Rogers, C. R. The Foundations of the Person-Centered Approach. Education 100, 98–107 (1979).
「診後說三句，更勝良帖十方」

@@

mindfulness and meditation for cancer
% 人的腦波一般分為β（12-30Hz）、α(8-12Hz）、θ(4-8Hz)、δ（1-4Hz)，四種波。當我們處於清醒、警覺狀態時，腦波是處於高頻率的β波。隨著身心狀態逐漸放鬆，卸下防衛時，腦波頻率也會逐漸下降至α、θ波，此時身心狀態是處於最寧靜、創造能力最好、對事情洞察能力最佳的狀態。如果能夠安祥進入睡眠階段，則腦波會降至δ波。靜坐時不僅可以使腦波由快速的β波降至α、θ波
In human EEG studies, cortical theta wave (4–7 Hz) tends to appear during meditative, drowsy, hypnotic or sleeping states in older children and adults. Theta is a frequency lower than consciousness. Theta is actually a brain function associated with imagination.

Warburg effect and carcinogenesis
cancer therapy by 患者自癒
Mindfullness Meditation help 復原力（resilience）
Self-Compassion  慈悲
Self-compassion 
除我執
 global self-esteem:
自戀（narcissism）1. Neff, K. D. & Vonk, R. Self-compassion versus global self-esteem: Two different ways of relating to oneself. J. Pers. 77, 23–50 (2009).\cite{Neff2009}
%%%% healing and cure
Reprogramming cells:
Environmental signals controlling cell behavior and cell behavior include genetics. The environmental signal via signal transduction can go into the nucleus and selectively change the reading of our gene, epigenetics regulation.

the membrane proteins and the chromosomal proteins that control the DNA, called regulatory proteins. But even those proteins are controlled by environmental signals. It is not DNA to RNA to protein.

The new understanding is: environmental signals to regulatory protein to DNA to RNA and then to protein.

療癒 There are studies that showed the genetic readout of some inflammatory genes in a group of people who then went through a meditation process. After 8 hours of meditation, the activity of the genes changed. 
You can change your genetic activity by how you change your response to the environment.

to recognize your perceptions, via signal transduction, are translated into biological behavior and your genetic activity.

Becoming aware of the subconscious source of our behavior gives us an opportunity to change our lives by rewriting the programs (in subconscious mind) of limitation or the things that interfere with us.

愛自己、蜜月；其實是 正念 mindfulness (因為自他不二）
You are creating a world of joy and love, and that’s called the honeymoon. When we fall in love, we stop focusing our conscious mind in thought and start keeping it present. 
It is called being mindful. 
You’ve been looking for yourself your whole life.
愛、性、正念止觀
Science has recognized that immediately after falling in love, we enter a period of mindfulness where we keep our conscious mind present.

You start running programs that are based on your conscious wishes and desires. All of a sudden, without the programs—without the subconscious programs—we begin to experience a heavenly life.
%%%%

情志養生 悲喜憂思苦 七情
人俯仰於天地之間
順從四季氣候變化
保養正氣陶冶性情
自我療癒身心靈疾病
%自他不二 心存正念 向內看，解決苦之源
%1.衷心懺悔
%2.真心感謝
%3.誠意祝福
%4.永存善念 慈悲
%5.心無恐懼: 情志養生
每位醫師都可以成為「創傷知情者」
幫助我們身邊的病患， 懂他的心靈創傷
讓他有安全感， 才有機會改變疾病的走向

@@

%%%%%% carcinomgenesis
95\% of cognitive behavior runs on subconscious program:

7\% 對於健康有不良影響 => 但是惡劣競爭下的生存技能
Of the downloaded behaviors acquired before age 7, the vast majority—70\% or more—are programs of limitation, disempowerment, and self-sabotage. These programs were acquired from other people, not from ourselves. Again, being subconscious, these programs are occurring without conscious recognition and awareness. 
It effects on epigenetic regulation.

Less than 1\% of disease is associated with genetics. Over 90\% of disease is a total reflection of environment and especially our programming: the disempowering, self-sabotaging behaviors that we acquired in the first 7 years.

Genes are not self-actualizing. The control of genes is not due to any inherent activity in the DNA itself. The change of genetic activity is due to the interaction of the cell with environmental signals.

the cell membrane through receptors picking up the signals and translating them into biology, which then sends signals into the nucleus, which then controls the genetic activity.

%%%%%

@@

*** TCPA with deep learning: gene expression on pathological section, or digital tissue microarray, TMA
佩戴可監測心率、體溫、血壓及其他關鍵數據的裝置，醫師也因此能夠獲得更多資料以更深入瞭解患者的病情，不再依靠病人的回憶進行判斷，診斷的準確性也會隨之提升。

在生物醫學領域，氨基酸或DNA等序列的使用可說是相當普遍，由於序列可視為一種具有隱性結構的語言，因此自然語言處理模型所採用的架構便可運用在理解並生成生物醫學領域的序列。
